---
output: html_document
runtime: shiny
---

<style>

body{
  font-family: Helvetica;
  font-size: 16pt;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<hr>

<!-- # OLS: Case 1 -->

# Linear Regression Model

<hr>

## Motivation

### Experiment No 01

Understand the effect of increasing the sample size on the sampling distribution of the slope coefficient of a linear regression model.

Change the number of observations $N$ to see the effect of the sample size $N$ on the properties of the OLS estimator for the slope coefficient $\beta_1$ of the linear regression model below.

<hr>

## Regression Model

We are interested in the sampling properties of the OLS estimator for the slope coefficient $\beta_1$ of the following linear regression model

\begin{align}
Y_i &= \beta_0 + \beta_1 X_i + u_i, \\
X_i &\sim U_{\left[a, b\right]}, \\
u_i &\sim N\left(0, \sigma_u\right).
\end{align}

<!-- X_i &\sim N\left(0, \sigma_X\right), \\ -->

<hr>

```{r tabsets, echo=FALSE}
shinyAppDir(
  "ols-case-xx-app",
  options = list(
    width = "100%", height = 700
  )
)
```

<hr>

## Interpretation

* ...
