---
output: html_document
runtime: shiny
---

<style>

body{
  font-family: Helvetica;
  font-size: 16pt;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<hr>

<!-- # OLS: Case 1 -->

# Linear Regression Model: Illustration No 01

<hr>

## Motivation

Understand the effect of increasing the sample size $N$ on the sampling distribution of the slope coefficient of a linear regression model.

<hr>

## Regression Model

<!-- This illustrations shows the sampling properties of the OLS estimator for the slope coefficient $\beta_1$ of the following linear regression model -->

We are interested in the sampling properties of the OLS estimator for the slope coefficient $\beta_1$ of the following linear regression model

\begin{align}
Y_i &= -2 + 3.5 X_i + u_i, \\
X_i &\sim N\left(0,10\right), \\
u_i &\sim N\left(0,10\right).
\end{align}

Change the number of observations $N$ to see the effect of the sample size $N$ on the properties of the OLS estimator for the slope coefficient $\beta_1$ of the linear regression model above.

<hr>

```{r tabsets, echo=FALSE}
shinyAppDir(
  "ols-case-01-app",
  options = list(
    width = "100%", height = 700
  )
)
```

<hr>

## Interpretation

* ...
